---
title: "blblm vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
library(tidyverse)
```

## blblm

### blblm(formula, data, m = 10, B = 5000)

This function is the core of the package. It helps you to set up the linear model.
* `formula`: an object of class "formula", a description of the model to be fitted.
* `data`: an optional data frame or list of file names, the data you want to use to fit the model.
* `m`: an integer indicating the number of subsamples you want to use in the Bag of Little Bootstraps.
* `b`: an integer indicating the number of bootstraps for each subsample.

Base on the original code, I extended this function by adding two features. The first feature is parallelization.
The current function will let the user to decide whether to use parallelization and how many cores to use. If the
number of cores that user enters exceeds the available cores of user's machine, the function will stop. 

The second feature is now the function can read files if `data` input is a string vector of filenames. It uses `vroom`
function to read data, so it supports multiple data format, such as .csv, .tsv, .fwf, etc.

Here is an example of using `blblm()` to read given file names and build the model with parallelization. For the sake of 
speed, I choose a small B value. In the real process, B should be greater than the value in the example
```{r}
file_names <- file.path("flights", list.files("flights"))

fit <- blblm(arr_delay ~ air_time + distance, data = file_names, m = 10, B = 50)
```

### print(x, ...)

This function simply print the linear model we fitted.
```{r}
print(fit)
```

### sigma(object, confidence = FALSE, level = 0.95, ...)

This function will tell user the standard deviation of the fitted model.
* `object`: the fitted model that belongs to class `blblm`.
* `confidence` boolean. If `confidence = TRUE`, the output will include a confidence interval specified by `level`.
* `level` a numeric value between 0 and 1, indicating level of confidence.

Following is an example of estimated sigma with confidence interval:
```{r}
sigma(fit, confidence = TRUE, level = 0.95)
```

### coef(object, ...)

This function returns the estimated coefficients of model's independent variables and intercept.
* `object`: the fitted model that belongs to class `blblm`.
```{r}
coef(fit)
```

### confint(object, parm = NULL, level = 0.95, ...)

This function returns the confidence intervals of estimated coefficients, which can be acquired by call `coef()`.
* `object`: the fitted model that belongs to class `blblm`.
* `parm`: a string or a string vector that specifies the specific variables that those we want confidence interval from.
* `level` a numeric value between 0 and 1, indicating level of confidence.

```{r}
confint(fit, parm = "air_time", level = 0.95)
```

### predict(object, new_data, confidence = FALSE, level = 0.95, ...)

This function returns the predicted outcome when given a set of new data.
* `object`: the fitted model that belongs to class `blblm`.
* `new_data`: the input data that we want to predict its result
* `confidence` a boolean parameter. If `confidence = TRUE`, the output will include a confidence interval specified by `level`.
* `level` a numeric value between 0 and 1, indicating level of confidence.
```{r}
predict(fit, data.frame(air_time = c(220, 100), distance = c(1500, 700)), confidence = TRUE)
```


## blbglm

Beside improving the base code, I also added a new function to fit the date into generalized linear model (glm).
A lot like the updated `blblm()` function, this function also support read file names and parallelization. Also, I kept
the class of this function's output as "blblm" so it will share all blblm's methods.

### blbglm(formula, data, family = "gaussian", m = 10, B = 5000)

A new parameter `family` is added to this function. This function is used to indicate the kernel we use for our generalized
linear model. For example, if input data is continuous, we could use `family = gaussian()`; if data is discrete, we 
could use `family = poisson()`; if we want binary outcome, we could use `family = binomial()`. To use this function, you can refer
back to the instructions in __blblm__ section. 